A coupled particle level set and Moment-of-fluid method for simulating multiphase flows with phase change \thanks{this material is based upon work supported by National Aeronautics and Space Administration under grant number 80NSSC20K0352}

### 2024-03-07 reviewreply.tex

%% get rid of autoindent   :setl noai nocin nosi inde=
\documentclass{letter}

\newcommand{\bmu}{\mbox{\boldmath $u$\unboldmath}}

\date{\today}

\begin{document}
\begin{letter}{
Communications on Applied Mathematics and Computation  \\
Dr. Chi-Wang Shu, Editor-in-Chief\\}

\opening{Dear Dr. Chi-Wang Shu}
Please find enclosed the revised version of our 
manuscript (CAMC-D-22-00243):
``An improved coupled level set and continuous 
moment-of-fluid method for simulating multiphase flows 
with phase change.''
We thank the reviewer for his/her comments and thoughts 
regarding improvement of our paper. 
In addition to the modifications in response to the reviewers'
suggestions, some improvements have been made to our paper.
\begin{enumerate}
\item The ``method overview'' (section 4.1 now) gives more details: e.g. about
$\Delta t$ and when the level set function is ``redistanced'' (every time step
after advection).  
\item Algorithmic details that can be found in our previous work has been 
  deleted (appropriate citations are kept): CISL advection, viscous solver,
  and projection solver (on AMR hierarchical grid).  We have kept the 
  discretization details of how the exact signed distance to the multi-material
  CMOF reconstructed interface is found (as this is a coupling step) 
  (section 4.3).
\item The added mass algorithm has been improved.  Section 5.4.1, ``Added
  Mass model for static freezing problem'' has been modified accordingly.
  All of the effected freezing results were recomputed (the results changed
  very little).
\end{enumerate}	
We believe that we have addressed all of the reviewers'
concerns; the changes are itemized in detail below.\par 
\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  
%%Also, we have hi-lighted the major
%%changes to our article in 
%%\textcolor{red}{red}.  Also, if most of a section was modified, we
%%hi-lighted just the section heading in \textcolor{red}{red}.
\par\noindent
Changes made in response to comments of the Reviewer: \par 
\begin{enumerate}
\item 
\begin{verbatim}
1- The introduction goes straight to the heart of the 
problem and therefore immediately leads the 
reader to the "action". I have personnaly 
enjoyed it, but I suggest that the authors provide 
some context about free boundary problem; otherwise, 
readers less current on the literature may be disoriented. 
\end{verbatim}
\par 
\vspace{0.5cm}
Response: \\
We have added a new section ``Background - deforming boundary problems in fluid mechanics'' which addresses the reviewers' comments.
\vspace{0.5cm}
\item 
\begin{verbatim}
2- The mathematical description of the different domains and 
interfaces use the level-set formalism but no introduction 
is given on the level-set representation. I also suspect 
that the level-set used is the signed distance function 
(at least reinitialized every x iterations)?
\end{verbatim}
\par 
\vspace{0.5cm}
Response: \\
We have added a new Figure to the paper (added to the new section) which
illustrates the level set distance function property.  Also we have
added in two different places exactly when the level set function is 
reinitialized.
\vspace{0.5cm}
\item 
\begin{verbatim}
3- Some of the section titles are not formatted correctly.
\end{verbatim}
\par 
\vspace{0.5cm}
Response: \\
We double checked all of the section titles and found that they were ok?
Please advise.
\end{enumerate}

\closing{On behalf of the authors, \\ Mark Sussman}

\end{letter}

\bibliography{references}
\bibliographystyle{plain}
\end{document}

### 2024-03-07 main.tex
title and abstract are updated

\title{An improved 
  coupled level set and continuous moment-of-fluid method 
  for simulating multiphase flows with phase change
  \thanks{this material is based upon work supported by National
   Aeronautics and Space Administration under grant number
   80NSSC20K0352}}

%%!!format authors properly
%\author{
%	LastName1, FirstName1\\
%	\texttt{first1.last1@xxxxx.com}
%	\and
%	LastName2, FirstName2\\
%	\texttt{first2.last2@xxxxx.com}
%}
\author{
  Ye, Zhouteng \\
  ZJUI Institute, Zhejiang University, Haining, China
  \and
  Estebe, Cody \\
  Dept. of math, FL State Univ. 
  \and
  Liu, Yang \\
  Dept. of Mech. Engr., FL State Univ.
  \and
  Vahab, Mehdi \\
  Mech. and Aero. Engr. Mathworks, Natick, MA
  \and
  Huang, Zeyu \\
  School of Aerospace Engineering, Tsinghua University
  \and
  Sussman, Mark \\
  Dept. of math, FL State Univ. 
  \and
  Moradikazerouni, Alireza \\
  Dept. of Mech. Engr., FL State Univ.
  \and
  Shoele, Kourosh  \\
  Dept. of Mech. Engr., FL State Univ.
  \and
  Lian, Yongsheng \\
  Dept. of Mech. Engr., U. of Louisville
  \and
  Ohta, Mitsuhiro \\
  Dept. of Mech. Sci, Tokushima University 
  \and
  Hussaini, M. Yousuff \\ 
  Dept. of math, FL State Univ. 
}

@@

ABSTRACT:
An improved algorithm for computing multiphase flows is presented in which the multimaterial Moment-Of-Fluid (MOF) algorithm for multiphase flows, initially described by Li et al (2015), is enhanced addressing existing MOF difficulties in computing solutions to problems in which surface tension forces are crucial for understanding salient flow mechanisms.  The Continuous Moment of Fluid (CMOF) method is motivated in this article.  The CMOF reconstruction method inherently removes the ``checkerboard instability'' that persists when using the MOF method on surface tension driven multiphase (multimaterial) flows.  The CMOF reconstruction algorithm is accelerated by coupling the CMOF method to the level set method and coupling the CMOF method to a Decision Tree machine learning algorithm.

Multiphase flow examples are shown in 2D, 3D axisymmetric ``RZ,'' and 3D coordinate systems.  Examples include two material and three material multiphase flows: bubble formation, the impingement of a liquid jet on a gas bubble in a cryogenic fuel tank, freezing, and liquid lens dynamics.
% Fred Stern -> reconstructed distance function coupled with VOF 
%%cite: Mukundan
\linenumbers
\section{Introduction}
We present an improved ``Continuous Moment-of-Fluid'' (CMOF) algorithm
for computing solutions to multiphase (multimaterial) flows.  We 
demonstrate the benefits of our new algorithm, beyond that of the 
current state-of-the-art, on these benchmark multiphase flow
problems:
bubble formation\cite{helsby1955behaviour} (see Section \ref{bubform}),
freezing\cite{hu2010icing} (see Section \ref{freezing_sec}), 
liquid lens\cite{MIAO2021109358} (see Section \ref{liqlens}),
and bubble dynamics in a Cryogenic fuel 
tank\cite{bentz1993low} (see Section \ref{TPCEsec}).

>>>>

\title{A coupled particle level set and Moment-of-fluid method 
  for simulating multiphase flows with phase change
  \thanks{this material is based upon work supported by National
   Aeronautics and Space Administration under grant number
   80NSSC20K0352}}

%%!!format authors properly
%\author{
%	LastName1, FirstName1\\
%	\texttt{first1.last1@xxxxx.com}
%	\and
%	LastName2, FirstName2\\
%	\texttt{first2.last2@xxxxx.com}
%}
\author{
  Estebe, Cody \\
  Dept. of math, FL State Univ. 
  \and
  Liu, Yang \\
  Dept. of Mech. Engr., FL State Univ.
  \and
  Sussman, Mark \\
  Dept. of math, FL State Univ. 
  \and
  Moradikazerouni, Alireza \\
  Dept. of Mech. Engr., FL State Univ.
  \and
  Shoele, Kourosh  \\
  Dept. of Mech. Engr., FL State Univ.
  \and
  Ohta, Mitsuhiro \\
  Dept. of Mech. Sci, Tokushima University 
}

@@

ABSTRACT:
An improved algorithm for computing multiphase flows is presented in 
which the multimaterial Moment-Of-Fluid (MOF) algorithm for multiphase flows, 
described by Li et al (2015), is enhanced with 
meshless particles.  The new method is less ``dissipative'' than the 
Continuous Moment of Fluid method (``CMOF,'' Ye at el (2023)) and inherently 
removes the ``checkerboard instability'' that persists when using the 
MOF method on surface tension driven multiphase (multimaterial) 
flows (Li et al (2015)).

Multiphase flow examples are shown in 2D, 3D axisymmetric ``RZ,'' and 
3D coordinate systems.  Examples include two material and three 
material multiphase flows: bubble formation, the impingement of a 
liquid jet on a gas bubble in a cryogenic fuel tank, freezing, melting,
evaporation, and liquid lens dynamics.
%%compare with Vu SI.
% Fred Stern -> reconstructed distance function coupled with VOF 
%%cite: Mukundan
\linenumbers
\section{Introduction}
We present an improved ``Continuous Moment-of-Fluid'' (CMOF) algorithm
for computing solutions to multiphase (multimaterial) flows.  We 
demonstrate the benefits of our new algorithm, beyond that of the 
current state-of-the-art, on these benchmark multiphase flow
problems:
bubble formation\cite{helsby1955behaviour} (see Section \ref{bubform}),
freezing\cite{hu2010icing} (see Section \ref{freezing_sec}), 
liquid lens\cite{MIAO2021109358} (see Section \ref{liqlens}),
and bubble dynamics in a Cryogenic fuel 
tank\cite{bentz1993low} (see Section \ref{TPCEsec}).
